Create Walkover of Brief Names

### 2022-04-09 data-cleaning/04-create-walkover-brief-name.Rmd
add missing brief

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")

@@

@@

```{r}
final %>% nrow()
```

>>>>

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus <- box_read("942789542605")

@@

Add missing case

```{r}
missing <- data.frame(new_id = 861822082999, case_code = 100,
           brief_code = 31,
           name_correct = "Planned Parenthood of Southeastern Pennsylvania v Casey. Amici Brief for Petitioners (feminist), by Pennsylvania Coalition against Domestic Violence & others - pared.DOCX",
           name_incorrect = "Amicus Brief for Petitioners (feminist), by |Pennsylvania Coalition Against Domestic Violence & others",
           old_id = 000000)

final <- final %>% rbind(missing)
```

@@

```{r}
final %>% distinct(new_id) %>% nrow()
```
